---
title: "2019-10-22 Horror Movies"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
theme_set(theme_light())
library(tidyverse)
library(skimr)
library(lubridate)
library(glue)
library(broom)
```

First of all, let's read in the data and view the columns we currently have

```{r raw_data}
horror_movies_raw <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-22/horror_movies.csv") 

head(horror_movies_raw,6)
```

From a quick glance it looks like we can make the following changes

* Convert release_date to date
* Extract year from title
* Seperate currency from budget column
* Extract minutes from movie_run_time
* Extract country from filming location
* Extract director from Plot

The following columns contain multiple entries so are difficult splitting out at this early stage. Might be worth splitting out if we try use xgbBoost to predict review_rating (for example).

* genres
* cast



```{r clean_data}
horror_movies <- horror_movies_raw %>% 
  extract(title,"year","\\((\\d\\d\\d\\d)\\)$",remove = FALSE,convert = TRUE) %>% 
  extract(plot,"directed_by","^Directed by (.*)\\.\\sWith",remove = FALSE) %>% 
  mutate(release_date = dmy(release_date),
         release_month = month(release_date),
         release_year = year(release_date),
         next_halloween = if_else(release_month > 10, 
                                  ymd(glue("{release_year +1}-10-31")),
                                  ymd(glue("{release_year}-10-31"))),
         days_before_halloween = next_halloween - release_date,
         currency = str_extract(budget,"^\\D*"),
         budget = parse_number(budget),
         filming_country = str_trim(str_extract(filming_locations,"(?!.*,).*$")), 
         movie_run_time_mins = parse_number(movie_run_time)
         ) 
  

  glimpse(horror_movies)
```

First question I have: does the review_ratings increase as the number of movies a director films increases?
```{r}
horror_movies1 <- horror_movies %>% 
  group_by(directed_by) %>% 
  mutate(directors_x_movie = rank(release_date,ties.method = "first")) %>% ungroup()


horror_movies1 %>% ggplot(aes(directors_x_movie)) + geom_density() # shows majority of direcors only film one horror movie
horror_movies1 %>% ggplot(aes(x = as_factor(directors_x_movie),y = review_rating)) + geom_boxplot()

```

Nope, there doesn't look to be much of a relationship. Let's compute an analysis of variance.

```{r}
horror_movies %>% lm(review_rating ~ directors_x_movie, data = .) %>% anova() %>% tidy()
```

This p value here indicates that the variance of review_rating cannot be explained by the number of movies a director has filmed.

```{r}
horror_movies %>% count(movie_run_time,sort = T)
fct_genres <- horror_movies %>% mutate(release_country = fct_lump(release_country,2))

fct_genres %>% mutate(no_rating = is.na(review_rating)) %>% ggplot(aes(release_date, fill = release_country)) + geom_histogram() + facet_wrap(~no_rating)

```

```{r}
horror_movies %>% lm(review_rating ~ release_country, data = .) %>% anova() %>% tidy()
```

```{r}
horror_movies %>% ggplot(aes(x = days_before_halloween)) + geom_histogram()
```

```{r}
horror_movies %>% ggplot(aes(review_rating)) + geom_density() + facet_wrap(~movie_rating)
shapiro.test(horror_movies$review_rating)
```



